Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2015-09-22 paper/letter.tex
adding best parameters

3. Rotation and the expected features.
It has been shown that rotation also imprints an effect on the
Lyman-alpha morphology. 
The most important consequence of rotation is that spherical 
symmetry is broken.
The line morphology now depends on the viewing angle respect to the
rotation axis.  
For a line sight perpendicular to the rotation axis the intensity and
the line center and the line width increase with rotational velocity. 
When the rotational velocity is close to the half-line width of the
static line, the line becomes single peaked as it is observed in
\tol, a unique feature that other theoretical models find
impossible to reproduce.

@@

TOL1214-277 was first observed by ... it is a compact 
dwarf galaxy and does not have old stars.

@@

Figure 1. Observed line + fit.

@@

We estimate the total neutral hydrogen mass to be $M\approx
m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a Hydrogen's atom, $\tau$ is
the optical depth and $n$ is the number density of neutral Hydrogen
atoms. For this system we estimate that for average values of
$n=1\times 10^3$ the total hydrogen mass is $M\times
10^{14}$M$_{\odot}$. However, blind HI surveys have put an upper limit
in the neutral hydrogen mass of ???

>>>>

3. Rotation and the expected features.
It has been shown that rotation also imprints an effect on the
Lyman-alpha morphology. 
The most important consequence of rotation is that spherical 
symmetry is broken.
The line morphology now depends on the viewing angle respect to the
rotation axis.  
For a line of sight perpendicular to the rotation axis the intensity and
the line center and the line width increase with rotational velocity. 
When the rotational velocity is close to the half-line width of the
static line, the line becomes single peaked as it is observed in
\tol, a unique feature that other theoretical models find
impossible to reproduce.

@@

\tol was first observed by ... it is a compact 
dwarf galaxy and does not have old stars.

@@

Figure 1. shows the observational data for \tol with the overplot from
our best fit model. The parameters for the best fit are
$v_{max}=300$kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K and a
viewing angle $\theta<30$ degrees.

Observed line + fit.

@@

We estimate the total neutral hydrogen mass to be $M\approx
m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a Hydrogen's atom, $\tau$ is
the optical depth, $\sigma$ is the cross section at the line's center
and $n$ is the number density of neutral Hydrogen atoms. For this
system we estimate that for average values of $n=1\times 10^3$ the
total hydrogen mass is $M\times 10^{14}$M$_{\odot}$. However, blind HI
surveys have put an upper limit in the neutral hydrogen mass of ???
